### 2018-05-29 submission/manuscript.Rmd
update first result section

***The Number of OTUs are Dependent on Polymerase:***
Differences in the range of the number of OTUs detected for fecal samples is dependent on the polymerase used [Figure 1]. Additionally, there is a trend for lower number of cycles (15-20) to result in a reduced range in the number of OTUs versus higher number of cycles (25, 30, and 35) for all polymerases [Figure 1]. There is an overall difference in the number of OTUs detected within fecal samples between polymerases at 35 cycles (F-stat > `r round(min(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "F.value"]), digits = 2)`, P-value = `r format(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "bh"], digits = 2, nsmall = 2, scientific = T)`) [Table S1]. No differences between the polymerases was found based on a Tukey post-hoc test (P-value `r ifelse(min(filter(fs_tukey_summary, sub_sample_level == 1000)[, "padj"]) > 0.05,  invisible(">"), invisible("check data"))` 0.05) [Table S2]. The polymerase dependent difference in the range of the number of OTUs also was observed in the mock community samples [Figure 2]. Regardless if fecal or mock communities were used, the same polymerases had high (Platinum) and low (Accuprime) number of OTUs and this was consistent across the number of cycles used [Figure 1-2 & Table S1-S4]. In contrast to the results obtained with fecal samples, differences between polymerases were observed as early as 20 cycles in the mock community (F-stat = `r round(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "F.value"], digits = 2)`, P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S1]. The majority of differences for the number of OTUs detected in the Mock community is largely due to Kappa and Platinum differences to the other polymerases across the different number of cycles [Table S2]. Based on these observations in fecal and mock communities, it is clear that different polymerases result in a different total number of OTUs within a sample.

@@

**Figure 1: Total Number of OTUs in Fecal Samples by Number of Cycles.** The x-axis represents the different number of cycles used and the y-axis is the number of OTUs. The legend represents the color code for the 5 different HiFi DNA polymerases used. The range in the number of OTUs detected in the different fecal samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases.

**Figure 2:  Total Number of OTUs in Mock Samples by Number of Cycles.** The x-axis represents the different number of cycles used and the y-axis is the number of OTUs. The legend represents the color code for the 5 different HiFi DNA polymerases used. The dotted black line represents the number of OTUs detected when only the references sequences are clustered. The range in the number of OTUs detected in the Mock samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases.

>>>>

***The Number of OTUs are Dependent on Polymerase:***
Differences in the range of the number of OTUs detected for fecal samples is dependent on the polymerase used (e.g. Accuprime at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_max)` versus Phusion at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`) [Figure 1]. Additionally, there is a trend for lower number of cycles (15-20) to result in a reduced range in the number of OTUs versus higher number of cycles (25, 30, and 35) for all polymerases (e.g. Phusion at 15 cycles = `r filter(fecal_numOTU_data, cycles == "15x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "15x", taq == "Phusion") %>% pull(taq_max)` versus Phusion at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`) [Figure 1]. There is an overall difference in the number of OTUs detected within fecal samples between polymerases at 35 cycles (F-stat > `r round(min(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "F.value"]), digits = 2)`, P-value = `r format(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "bh"], digits = 2, nsmall = 2, scientific = T)`) [Table S1]. Using a Tukey post-hoc test to identify which polymerase groups were different from each other at 35 cycles, no difference was found (P-value `r ifelse(min(filter(fs_tukey_summary, sub_sample_level == 1000)[, "padj"]) > 0.05,  invisible(">"), invisible("check data"))` 0.05) [Table S2]. The polymerase dependent difference in the range of the number of OTUs also was observed in the mock community samples [Figure 2]. The closest the polymerases came to the total of `r pull(ref_mock_otu_num, numOtus)` OTUs created by the mock reference 16S sequences was at 25 and 30 cycles [Figure 2]. Regardless of if fecal or mock communities were used, the same polymerases generated high and low number of OTUs and this was consistent across the number of cycles used [Figure 1-2 & Table S1-S2].  In contrast to the results obtained with fecal samples, differences between polymerases for the number of OTUs created were observed as early as 20 cycles in the mock community (F-stat = `r round(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "F.value"], digits = 2)`, P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S1]. Using a Tukey post-hoc test, the majority of differences for the number of OTUs detected in the mock community is largely due to Kappa and Platinum differences versus the other polymerases across the different number of cycles [Table S2]. Based on these observations in fecal and mock communities, it is clear that using different polymerases result in a different total number of OTUs within a sample.

@@

**Figure 1: Total Number of OTUs in Fecal Samples by Number of Cycles.** The x-axis represents the different number of cycles used and the y-axis is the number of OTUs. The points represent the median value of all four fecal samples. The lines represent the range of the minimum and maximum number of OTUs detected within the four fecal samples. The range in the number of OTUs detected in the different fecal samples increased as cycle number increased. This increased range also was larger for specific HiFi DNA polymerases.

**Figure 2:  Total Number of OTUs in Mock Samples by Number of Cycles.** The x-axis represents the different number of cycles used and the y-axis is the number of OTUs. The points represent the median value of all four fecal samples. The lines represent the range of the minimum and maximum number of OTUs detected within the four fecal samples. The dotted black line represents the number of OTUs detected when only the references sequences for the mock community are clustered. The range in the number of OTUs detected in the mock samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases.

### 2018-05-29 submission/manuscript.tex
update first result section

\textbf{\emph{The Number of OTUs are Dependent on Polymerase:}}
Differences in the range of the number of OTUs detected for fecal
samples is dependent on the polymerase used {[}Figure 1{]}.
Additionally, there is a trend for lower number of cycles (15-20) to
result in a reduced range in the number of OTUs versus higher number of
cycles (25, 30, and 35) for all polymerases {[}Figure 1{]}. There is an
overall difference in the number of OTUs detected within fecal samples
between polymerases at 35 cycles (F-stat \textgreater{} 16.35, P-value =
9.7e-05) {[}Table S1{]}. No differences between the polymerases was
found based on a Tukey post-hoc test (P-value \textgreater{} 0.05)
{[}Table S2{]}. The polymerase dependent difference in the range of the
number of OTUs also was observed in the mock community samples {[}Figure
2{]}. Regardless if fecal or mock communities were used, the same
polymerases had high (Platinum) and low (Accuprime) number of OTUs and
this was consistent across the number of cycles used {[}Figure 1-2 \&
Table S1-S4{]}. In contrast to the results obtained with fecal samples,
differences between polymerases were observed as early as 20 cycles in
the mock community (F-stat = 15.82, P-value = 0.002) {[}Table S1{]}. The
majority of differences for the number of OTUs detected in the Mock
community is largely due to Kappa and Platinum differences to the other
polymerases across the different number of cycles {[}Table S2{]}. Based
on these observations in fecal and mock communities, it is clear that
different polymerases result in a different total number of OTUs within
a sample.

@@

\textbf{Figure 1: Total Number of OTUs in Fecal Samples by Number of
Cycles.} The x-axis represents the different number of cycles used and
the y-axis is the number of OTUs. The legend represents the color code
for the 5 different HiFi DNA polymerases used. The range in the number
of OTUs detected in the different fecal samples increased as cycle
number increased. This range was also larger for specific HiFi DNA
polymerases.

\textbf{Figure 2: Total Number of OTUs in Mock Samples by Number of
Cycles.} The x-axis represents the different number of cycles used and
the y-axis is the number of OTUs. The legend represents the color code
for the 5 different HiFi DNA polymerases used. The dotted black line
represents the number of OTUs detected when only the references
sequences are clustered. The range in the number of OTUs detected in the
Mock samples increased as cycle number increased. This range was also
larger for specific HiFi DNA polymerases.

>>>>

\textbf{\emph{The Number of OTUs are Dependent on Polymerase:}}
Differences in the range of the number of OTUs detected for fecal
samples is dependent on the polymerase used (e.g.~Accuprime at 35 cycles
= 84 - 106 versus Phusion at 35 cycles = 84 - 136) {[}Figure 1{]}.
Additionally, there is a trend for lower number of cycles (15-20) to
result in a reduced range in the number of OTUs versus higher number of
cycles (25, 30, and 35) for all polymerases (e.g.~Phusion at 15 cycles =
10 - 19 versus Phusion at 35 cycles = 84 - 136) {[}Figure 1{]}. There is
an overall difference in the number of OTUs detected within fecal
samples between polymerases at 35 cycles (F-stat \textgreater{} 16.35,
P-value = 9.7e-05) {[}Table S1{]}. Using a Tukey post-hoc test to
identify which polymerase groups were different from each other at 35
cycles, no difference was found (P-value \textgreater{} 0.05) {[}Table
S2{]}. The polymerase dependent difference in the range of the number of
OTUs also was observed in the mock community samples {[}Figure 2{]}. The
closest the polymerases came to the total of 8 OTUs created by the mock
reference 16S sequences was at 25 and 30 cycles {[}Figure 2{]}.
Regardless of if fecal or mock communities were used, the same
polymerases generated high and low number of OTUs and this was
consistent across the number of cycles used {[}Figure 1-2 \& Table
S1-S2{]}. In contrast to the results obtained with fecal samples,
differences between polymerases for the number of OTUs created were
observed as early as 20 cycles in the mock community (F-stat = 15.82,
P-value = 0.002) {[}Table S1{]}. Using a Tukey post-hoc test, the
majority of differences for the number of OTUs detected in the mock
community is largely due to Kappa and Platinum differences versus the
other polymerases across the different number of cycles {[}Table S2{]}.
Based on these observations in fecal and mock communities, it is clear
that using different polymerases result in a different total number of
OTUs within a sample.

@@

\textbf{Figure 1: Total Number of OTUs in Fecal Samples by Number of
Cycles.} The x-axis represents the different number of cycles used and
the y-axis is the number of OTUs. The points represent the median value
of all four fecal samples. The lines represent the range of the minimum
and maximum number of OTUs detected within the four fecal samples. The
range in the number of OTUs detected in the different fecal samples
increased as cycle number increased. This increased range also was
larger for specific HiFi DNA polymerases.

\textbf{Figure 2: Total Number of OTUs in Mock Samples by Number of
Cycles.} The x-axis represents the different number of cycles used and
the y-axis is the number of OTUs. The points represent the median value
of all four fecal samples. The lines represent the range of the minimum
and maximum number of OTUs detected within the four fecal samples. The
dotted black line represents the number of OTUs detected when only the
references sequences for the mock community are clustered. The range in
the number of OTUs detected in the mock samples increased as cycle
number increased. This range was also larger for specific HiFi DNA
polymerases.
